SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-27 scipy-1.0/paper.tex
Second round of revisions based on reviewer feedback in manuscript PR 43.

\texttt{scipy.sparse} offers seven sparse matrix data structures. 
The most important ones are CSR and CSC; these offer fast row or column 
access and fast matrix-vector multiplication, and are used heavily in 
scikit-learn.

@@

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively.

>>>>

\texttt{scipy.sparse} offers seven sparse matrix data structures,
also known as sparse formats. The most important ones are the row- 
and column-compressed formats (CSR and CSC, respectively). 
These offer fast major-axis indexing and fast matrix-vector multiplication,
and are used heavily in scikit-learn.

@@

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively. Also, we've made a concerted effort to bring the
\texttt{scipy.sparse} API into line with the equivalent NumPy API where possible,
typically by adding support for kwargs like axis=None or copy=False to many methods.
